---
title: "Topic ideas"
subtitle: "STA 210 - Project"
author: "Ginger and Stats - Rakshita Ramakrishna, Aimi Wen, Nathan Nguyen, Bryan Pan"
format: pdf
editor: visual
---

```{r warning = F, message = F}
#| label: load-packages

library(tidyverse)
```

# Project idea 1

## Introduction and data

-   The source of the dataset is from the Board Game Geek website through the tidy tuesday package. A larger dataset can be found on Kaggle.

-   The data was collected through crowd-sourced ratings posted on the Board Game Geek website over the span of various years, but for our analysis we will only focus on ratings during the year 2016. 

-   The data actually belongs to 2 datasets (ratings and details), one contains the technical information (rules, category, descriptions, etc.) of the board games, and more details on the number of users owning them, and the another contains the information of data rating with numbers of users rated the board game. We plan to combine the datasets together. There are a lot of variables associated with the data, but for our own interest and for the research questions we want to answer, these variables/characteristics are the most important:

    -   `average`: variable of `ratings.csv`, the rating of user on a scale from 0 to 10.

    -   `minplayer, maxplayer, minplaytime, maxplaytime, playingtime, minage:` variables of `details.csv`, the characteristics of the games, including min/max players allowed, min/max playing time allowed, playing time estimate of the game, and minimum age allowed. These are based on the rules of the game.

    -   `users_rated`: a variable of `ratings.csv`, the number of users rated the games.

    -   `owned`: a variable of `details.csv`, the number of people who have the games.

    -   year of being published, category, and game mechanic could also contribute to the analysis.

    <!-- -->

    -   Though the data is split between two separated datasets, we will perform a merge of the two together to make our analysis easier. In both datasets, we have game id and name. We will use that to merge the 2 datasets. Also, because there are so many different observations, we plan to filter out only board games published in one specific year, which we initially agree to choose the year 2016, and this is also to avoid dependency on time.

## Research question

-   What can predict Board Game rating and popularity (measured by number of user ratings)? How can we use features of the games, and number of users play the games to predict those outcomes?

## Glimpse of data

```{r warning = F, message = F}
#| label: data-1

details <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-01-25/details.csv')

ratings <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-01-25/ratings.csv')

glimpse(ratings)
glimpse(details)
```

\pagebreak

# Project idea 2

## Introduction and data

-   The dataset comes from Flavors of Cocoa:

    -   <http://flavorsofcacao.com/chocolate_database.html>

    -   The Manhattan Chocolate Society collected the data, and the dataset contains reviews of over 2,500 plain chocolate bars from 2006 to 2021. Each row represents a plain chocolate bar, and the columns represents characteristics of the chocolate bar. From the flavors of cocoa website, it looks like the subjective variables are from the tasters that are part of the society, while the objective observations are from the chocolate manufacturers.

-   Data is being continuously collected and added to the dataset after chocolate bars are reviewed. The reviews started in 2006 and have continued until 2021.

-   As mentioned above, the data can be broken into 2 groups: subjective and objective.

    -   The subjective observations include rating and most memorable characteristics. These are determined by the tasters form the Manhattan Chocolate society.

        -   The rating system can found here: <http://flavorsofcacao.com/review_guide.html>

        -   As a summary, the rating scale is:

            -   4.0-5.0 = Outstanding

            -   3.5-3.9= Highly Recommended

            -   3.0-3.49= Recommended

            -   2.0-2.9= Disappointing

            -   1.0-1.9= Unpleasant

    -   The objective observations are descriptions given by the chocolate manufacturer themselves. These observations include: country of bean origin, percent of cocoa for each chocolate bar, ingredients, company, and company location.

## Research question

-   What characteristics can predict chocolate ratings?

## Glimpse of data

```{r warning = F, message = F}
#| label: data-2

chocolate <- read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-01-18/chocolate.csv')

glimpse(chocolate)
```

\pagebreak
