---
title: "Topic ideas"
subtitle: "STA 210 - Project"
author: "Ginger and Stats - Rakshita Ramakrishna, Aimi Wen, Nathan Nguyen, Bryan Pan"
format: pdf
editor: visual
---

```{r warning = F, message = F}
#| label: load-packages

library(tidyverse)
```

# Project idea 1

## Introduction and data

-   State the source of the data set.

    -   The source of the dataset is from the Board Game Geek website through the tidy tuesday package. A larger dataset can be found on Kaggle.

-   Describe when and how it was originally collected (by the original data curator, not necessarily how you found the data)

    -   The data was collected through crowd-sourced ratings posted on the Board Game Geek website over the span of various years, but for our analysis we will only focus on ratings during the year 2016. 

-   Describe the observations and the general characteristics being measured in the data

    -   The data is splitted into two datasets, one contains the technical information of the board games, and more details on the number of users owning them.

## Research question

-   Describe a research question you're interested in answering using this data.

## Glimpse of data

-   Use the `glimpse` function to provide an overview of the dataset

```{r warning = F, message = F}
#| label: data-1

details <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-01-25/details.csv')

ratings <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-01-25/ratings.csv')

glimpse(ratings)
glimpse(details)
```

\pagebreak

# Project idea 2

## Introduction and data

-   State the source of the data set.

-   Describe when and how it was originally collected (by the original data curator, not necessarily how you found the data)

-   Describe the observations and the general characteristics being measured in the data

## Research question

-   Describe a research question you're interested in answering using this data.

## Glimpse of data

-   Use the `glimpse` function to provide an overview of the dataset

```{r}
#| label: data-2

chocolate <- read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-01-18/chocolate.csv')

glimpse(chocolate)
```

\pagebreak

# Project idea 3

::: callout-important
Project idea 3 is optional. If you decide to submit only 2 ideas, please delete the section headings below and leave a note below stating so. If you decide to submit the 3rd idea, please delete this callout.
:::

## Introduction and data

-   State the source of the data set.

-   Describe when and how it was originally collected (by the original data curator, not necessarily how you found the data)

-   Describe the observations and the general characteristics being measured in the data

## Research question

-   Describe a research question you're interested in answering using this data.

## Glimpse of data

-   Use the `glimpse` function to provide an overview of the dataset

```{r}
#| label: data-3

# add code to load and glimpse data here
```
