---
title: "Topic ideas"
subtitle: "STA 210 - Project"
author: "Ginger and Stats - Rakshita Ramakrishna, Aimi Wen, Nathan Nguyen, Bryan Pan"
format: pdf
editor: visual
---

```{r warning = F, message = F}
#| label: load-packages

library(tidyverse)
```

# Project idea 1

## Introduction and data

-   State the source of the data set.

    -   The source of the dataset is from the Board Game Geek website through the tidy tuesday package. A larger dataset can be found on Kaggle.

-   Describe when and how it was originally collected (by the original data curator, not necessarily how you found the data)

    -   The data was collected through crowd-sourced ratings posted on the Board Game Geek website over the span of various years, but for our analysis we will only focus on ratings during the year 2016. 

-   Describe the observations and the general characteristics being measured in the data

    -   The data is splitted into two datasets, one contains the technical information of the board games, and more details on the number of users owning them.

## Research question

-   Describe a research question you're interested in answering using this data.

## Glimpse of data

-   Use the `glimpse` function to provide an overview of the dataset

```{r warning = F, message = F}
#| label: data-1

details <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-01-25/details.csv')

ratings <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-01-25/ratings.csv')

glimpse(ratings)
glimpse(details)
```

\pagebreak

# Project idea 2

## Introduction and data

-   The dataset comes from Flavors of Cocoa:

    -   <http://flavorsofcacao.com/chocolate_database.html>

    -   The Manhattan Chocolate Society collected the data, and the dataset contains reviews of over 2,500 plain chocolate bars from 2006 to 2021. Each row represents a plain chocolate bar, and the columns represents characteristics of the chocolate bar. From the flavors of cocoa website, it looks like the subjective variables are from the tasters that are part of the society, while the objective observations are from the chocolate manufacturers.

-   Data is being continuously collected and added to the dataset after chocolate bars are reviewed. The reviews started in 2006 and have continued until 2021.

-   As mentioned above, the data can be broken into 2 groups: subjective and objective.

    -   The subjective observations include rating and most memorable characteristics. These are determined by the tasters form the Manhattan Chocolate society.

        -   The rating system can found here: <http://flavorsofcacao.com/review_guide.html>

        -   As a summary, the rating scale is:

            -   4.0-5.0 = Outstanding

            -   3.5-3.9= Highly Recommended

            -   3.0-3.49= Recommended

            -   2.0-2.9= Disappointing

            -   1.0-1.9= Unpleasant

    -   The objective observations are descriptions given by the chocolate manufacturer themselves. These observations include: country of bean origin, percent of cocoa for each chocolate bar, ingredients, company, and company location.

## Research question

-   What characteristics can predict chocolate ratings?

## Glimpse of data

-   Use the `glimpse` function to provide an overview of the dataset

```{r}
#| label: data-2

chocolate <- read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-01-18/chocolate.csv')

glimpse(chocolate)
```

\pagebreak

# Project idea 3

::: callout-important
Project idea 3 is optional. If you decide to submit only 2 ideas, please delete the section headings below and leave a note below stating so. If you decide to submit the 3rd idea, please delete this callout.
:::

## Introduction and data

-   State the source of the data set.

-   Describe when and how it was originally collected (by the original data curator, not necessarily how you found the data)

-   Describe the observations and the general characteristics being measured in the data

## Research question

-   Describe a research question you're interested in answering using this data.

## Glimpse of data

-   Use the `glimpse` function to provide an overview of the dataset

```{r}
#| label: data-3

# add code to load and glimpse data here
```
