---
title: "Draft"
subtitle: "STA 210 - Project"
<<<<<<< HEAD
author: "Ginger and Stats - Aimi Wen, Rakshita Ramakrishna, Nathan Nguyen"
=======
author: "Ginger and Stats - Aimy Wen, Rakshita Ramakrisna, Nathan Nguyen"
>>>>>>> 9fd406477b3755d85fde6d5265108577a418639a
format: pdf
editor: visual
---

```{r}
#| label: load-pkg-data
#| warning: false
library(tidyverse)
library(tidymodels)
library(tidytext)

<<<<<<< HEAD
chocolate <- read_csv("../data/chocolate.csv")
=======
chocolate <- read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-01-18/chocolate.csv')
>>>>>>> 9fd406477b3755d85fde6d5265108577a418639a
```

# Exploratory Data Analysis

<<<<<<< HEAD
## Data description

## Analysis approach

```{r}
chocolate <- chocolate %>%
  mutate(lecithin = case_when(
    grepl("L", ingredients) ~ 1,
    T ~ 0
  ),
  vanilla = case_when(
    grepl("V", ingredients) ~ 1,
    T ~ 0
  ),
  cocoa = case_when(
    grepl("C", ingredients) ~ 1,
    T ~ 0
  ),
  salt = case_when(
    grepl("Sa", ingredients) ~ 1,
    T ~ 0
  )
  )
```

```{r}
chocolate %>%
  filter(grepl("*", ingredients)) %>%
  select(ingredients)
```

```{r}
chocolate %>%
  drop_na(
    ingredients
  )
```
=======
...

## Shape of Ratings (already done)

...

## Cocoa Percent (Aimi)

```{r}
#| label: cocoa-percent

chocolate$cocoa_percent <- as.numeric(gsub('[,%]', '', chocolate$cocoa_percent))

chocolate$rating <- as.character(chocolate$rating) 

ggplot(data= chocolate, aes(x= cocoa_percent)) + geom_histogram() 

ggplot(data= chocolate, aes(x= cocoa_percent, y= rating)) + geom_boxplot()

chocolate$rating <- as.numeric(chocolate$rating) 


```

## Ingredients (Nathan)

## Most Memorable Characteristic (Aimi)

```{r}
#| label: memorable-char

tidy_chocolate<- chocolate %>% unnest_tokens(word, most_memorable_characteristics)

tidy_chocolate %>% 
  group_by(word) %>% 
  summarize( n= n(), 
             rating= mean(rating) ) %>%
  ggplot(aes(n, rating)) + 
  geom_hline(yintercept= mean(chocolate$rating)) + 
  geom_jitter(color= "blue", alpha= 0.5) + 
  geom_text(aes(label= word),
            check_overlap= TRUE, 
            family= "IBMPlexSans", 
            vjust= "top", 
            hjust= "left") +
  scale_x_log10() 
```

## Country Bean of Origin vs Specific Bean Origin (Rakshita)
>>>>>>> 9fd406477b3755d85fde6d5265108577a418639a

## Company Location (Rakshita)

<<<<<<< HEAD
The data dictionary can be found [here](ADD%20LINK!!!).
=======
## Review Date (Nathan)
>>>>>>> 9fd406477b3755d85fde6d5265108577a418639a
